\sys: Light-touch Data-Parallel Shell Processing

### 2020-10-08 paper/draft.tex
Update DFG figure

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{\detokenize{./figs/pash_dfg.pdf}}
  \vspace{-25pt}
  \caption{
    \textbf{From Shell script AST to DFGs.}
    The AST on the left has two dataflow regions, each not extending beyond \ttiny{&&}~\cf{dataflow-regions}.
    \nv{DFG2 reads from f2, grep writes to f3}
  }
  \vspace{-15pt}
  \label{fig:ast-dfg}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{\detokenize{./figs/unix50_individual_speedups_16.pdf}}
  \caption{
	  \textbf{Unix50 scripts.}
    Speedup (left axis) over sequential execution (right axis) for Unix50 scripts.
    Parallelism is 16$\times$ on 10GB of input data~\cf{unix50}.
    Pipelines are sorted in descending speedup order.\str
    % \kk{Add speedup by primitives and transformations in bar-chart.}
    % The solid line indicates the average speedup $\times5.49$ and the dotted line indicates 1.
    % \nv{Idea: scripts that only take over 0.01s?}
    % \kk{Now that we removed the small ones, sequential time does not add a lot to this plot. Maybe we can just show speedups?}
  }
  \vspace{-15pt}
  \label{fig:unix50-individual}
\end{figure}

@@

Concurrent to our work, POSH~\cite{raghavan2020posh} is a framework for running shell scripts over remote storage by offloading the I/O-intensive portions to proxy servers closer to the data.
POSH focuses on colocating distributed operation, and introduces a novel scheduling algorithm. 
\sys instead focuses on the parallelization of CPU-intensive scripts, by transforming them to DFGs, applying transformations, and then transforming them back to parallel schell scripts augmented with \sys's runtime primitives to be executed on a standard shell.
%  non-distributed parallelism, is location-agnostic, and focuses on correctness through its dataflow transformations.

@@

Dryad~\cite{isard2007dryad} is a distributed system for dataflow graphs. Dryad offers a scripting language, Nebula, that allows using shell commands such as \ttt{grep} or \ttt{sed} in place of individual dataflow nodes. The main difference with \sys is that in Dryad the programmer needs to explicitly express the data flow graph, which is then executed in a distributed fashion, whereas Pash automatically parallelizes a given shell script by producing a parallel script that runs on an unmodified shell of choice.

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{\detokenize{./figs/pash_dfg.pdf}}
  \vspace{-25pt}
  \caption{
    \textbf{From Shell script AST to DFGs.}
    The AST on the left has two dataflow regions, each not extending beyond \ttiny{&&}~\cf{dataflow-regions}.
  }
  \vspace{-15pt}
  \label{fig:ast-dfg}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{\detokenize{./figs/unix50_individual_speedups_16.pdf}}
  \caption{
	  \textbf{Unix50 scripts.}
    Speedup (left axis) over sequential execution (right axis) for Unix50 scripts.
    Parallelism is 16$\times$ on 10GB of input data~\cf{unix50}.
    Pipelines are sorted in descending speedup order. % \str
    % \kk{FUTURE: Add speedup by primitives and transformations in bar-chart.}
    % The solid line indicates the average speedup $\times5.49$ and the dotted line indicates 1.
    % \nv{Idea: scripts that only take over 0.01s?}
    % \kk{Now that we removed the small ones, sequential time does not add a lot to this plot. Maybe we can just show speedups?}
  }
  \vspace{-15pt}
  \label{fig:unix50-individual}
\end{figure}

@@

Concurrent to our work, POSH~\cite{raghavan2020posh} is a framework for running shell scripts over remote storage by offloading the I/O-intensive portions to proxy servers closer to the data.
POSH focuses on co-locating distributed operation, and introduces a novel scheduling algorithm. 
\sys instead focuses on the parallelization of CPU-intensive scripts, by transforming them to DFGs, applying transformations, and then transforming them back to parallel schell scripts augmented with \sys's runtime primitives to be executed on a standard shell.
%  non-distributed parallelism, is location-agnostic, and focuses on correctness through its dataflow transformations.

@@

Dryad~\cite{isard2007dryad} is a distributed system for dataflow graphs. Dryad offers a scripting language, Nebula, that allows using shell commands such as \ttt{grep} or \ttt{sed} in place of individual dataflow nodes. The main difference with \sys is that in Dryad the programmer needs to explicitly express the dataflow graph, which is then executed in a distributed fashion, whereas Pash automatically parallelizes a given shell script by producing a parallel script that runs on an unmodified shell of choice.
